

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Inertia Project  

The Inertia Project is a project initialized by Michael Greenacre to study the inertia values of Correspondence Analysis (CA).

## File outline

 **data** Results of computations
**miscellaneous** Script and information provided by Michael Greenacre
**compute_inertias.R** Functions to compute inertia summaries for rectangular frequency tables.
**plotting.R** Plotting functions to study the results of computations

## (Very) preliminary results  

These are very crude drafts.  

```{r}
# The commeted lines can be run to compute the results
source("plotting.R")
source("compute_inertias.R")
# categories <- c(3:9, seq(10, 90, 10), seq(100, 1000, 100))
# inertias <- compute_inertias(categories)
# save(file = "data/inertias.Rda", inertias)
inertias <- get(load("data/inertias.Rda"))
```

Inertia values were computed for rectangular tables of sizes `r colnames(inertias$first)`.
The results are in a list of matrices.

```{r}
str(inertias)
```

### Diagonals of the result matrices

The diagonals of the result matrices correspond to results from square tables.

```{r}
sq_first <- diag(inertias$first) # first eigenvalues
sq_total <- diag(inertias$others) + sq_first # sum of eigenvalues
plot_inertias(sq_first, sq_total, r = 1/3)
```

### Contour plot of first inertias of rectangular tables

```{r}
first <- inertias$first
contour(first, main = "Countour plot of first inertias of rectangular tables", sub = paste(colnames(first), collapse = " "))
```

